### 2016-12-01 paper/chapters/abstract.tex
minor grammatic fixes

\section{Abstract}
\label{sec:abstract}
Deep Learning has advanced at an incredible speed the last few years and has achieved human-level performance in some discrimination and classification tasks (object recognition, speech recognition).
These supervised methods have the huge drawback of requiring a vast amount of labeled data which is often expensive or unfeasible to obtain.
Learning hidden structure from unlabelled data known as unsupervised learning has had less of an impact recently.
However, it can be argued that this learning is most similar to human learning, in particular inferring information from observations and building an appropriate model from it.
We will discuss and explore some models for performing aforementioned inference as well as generating new data from these representations.
Building reasonable representation of the world from unlabelled data is arguably one of the key aspects to machine intelligence.
%However one of the key aspects to machine intelligence is learning a rich (?) model about the world and draw conclusions from it.
%The above mentioned tasks require huge amount of labelled data to perform well, which is one of the restrictions of these supervised learning mechanisms.
%Unsupervised learning has the potential to make use of the vast unlabelled data surrounding the world.
%This data can be used to learn representations

>>>>

\section{Abstract}
\label{sec:abstract}
Deep Learning has advanced at an incredible speed the last few years and has achieved human-level performance in some discrimination and classification tasks (object recognition, speech recognition).
These supervised methods have the huge drawback of requiring a vast amount of labelled data which is often expensive or unfeasible to obtain.
Learning hidden structure from unlabelled data known as unsupervised learning has had less of an impact recently.
However, it can be argued that this method is most similar to human learning, in particular inferring information from observations and building an appropriate model from it.
We will discuss and explore some models for performing this inference as well as generating new data from these representations.
Building reasonable representation of the world from unlabelled data is arguably one of the key aspects of machine intelligence.
%However one of the key aspects to machine intelligence is learning a rich (?) model about the world and draw conclusions from it.
%The above mentioned tasks require huge amount of labelled data to perform well, which is one of the restrictions of these supervised learning mechanisms.
%Unsupervised learning has the potential to make use of the vast unlabelled data surrounding the world.
%This data can be used to learn representations
